Retrofitting Effect Handlers onto OCaml

### 2020-10-28 retro-concurrency.tex
Updates

value ocaml_to_c (value unit) {
  caml_callback(*caml_named_value("c_to_ocaml"), Val_unit);
  return Val_int(0);
}
		\end{lstlisting}
    \subcaption{\texttt{meander.c}}
    \label{code:meander_c}
	\end{minipage}
\end{minipage}
  \begin{minipage}{0.39\linewidth}
    \centering
    \includegraphics[scale=0.5]{figures/stock_stack}
    \subcaption{Stack layout before raising exception.}
    \label{fig:stock_stack}
  \end{minipage}
\end{figure*}

@@

@@

@@

In order to forward exceptions across C frames, the C stub function
|caml_start_program|, which is the entry point for both the main OCaml code and
callbacks into OCaml, pushes an exception handler frame that forwards the
exception the innermost OCaml exception handler (|raised_exn_c| in
Figure~\ref{fig:stock_stack}), or prints a fatal error (|fatal_error|) if there
are no enclosing handlers. Exceptions are so cheap in OCaml that it is very
common to use them for \emph{local} control flow.

>>>>

value ocaml_to_c (value unit) {
  caml_callback(*caml_named_value("c_to_ocaml"), Val_unit);
  return Val_int(0);
}
		\end{lstlisting}
    \subcaption{\texttt{meander.c}}
    \label{code:meander_c}
	\end{minipage}
\end{minipage}
	\begin{minipage}{0.39\linewidth}
    \centering
    \includegraphics[scale=0.46]{figures/stock_stack}
    \subcaption{Stack layout before raising exception.}
    \label{fig:stock_stack}
  \end{minipage}
	\caption{Program stack on stock OCaml.}
\end{figure*}

@@

\subsection{External calls and callbacks}

@@

\subsection{Exception handlers}

@@

In order to forward exceptions across C frames, the C stub function
|caml_start_program|, which is the entry point for both the main OCaml code and
callbacks into OCaml, pushes an exception handler frame that forwards the
exception the innermost OCaml exception handler (|raised_exn_c| in
Figure~\ref{fig:stock_stack}), or prints a fatal error (|fatal_uncaught|) if there
are no enclosing handlers. Exceptions are so cheap in OCaml that it is very
common to use them for \emph{local} control flow.
